A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-04-24 ms.tex
Moved appendix into text.  switched order of spectral fitting and absolute flux calibration subsections

@@

% XXX incorporate
Given the shortcomings in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.

@@

@@

@@

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
% XXX clarify why one source used here, and more sources later 
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

@@

@@

@@

\section*{Appendix: Model Fitting}
% XXX this should be in main body, not an appendix

In general an experiment measures data $D$ and given some model of the
statistics of the measurement one usually assigns an error bar defining the
probability of getting that data, given a model $M$.  Given all the new data,
and prior data, there will be a new optimal set of model parameters $M$ with
associated error bars.  In general, these error bars are a parameterization of
a probability distribution function.  The pdf associated with the data often
called the likelihood ($\mathcal{L}$), while the one corresponding the model
error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
are related

Direct calculation of the posterior is difficult, particularly the
normalization factor, however there is a simple procedure for drawing samples
from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
Given any current location in parameter space, this algorithm draws a new set
of parameters and computes the relative likelihood increase. If the probability
difference is larger than a number drawn randomly from the set $(0:1]$, the
jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
such steps, this process has been shown to converge on the true posterior
distribution.  In practice it is run for a large number of steps until things
appear to stabilize. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

In \S \ref{sec:fits} we fit a spectral power law to catalog values by sampling
a (log) likelihood which assumes Gaussian measurement errors

A single overall flux scale is computed in a similar way. However, here we add
a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
several sources.

>>>>

% XXX remove references to appendix

@@

% XXX incorporate
Given the shortcomings in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
In this section, we describe ... % XXX

@@

% XXX in this section, we describe the details of data analysis used ...
% XXX connect to Parsons2010,2013, pober2013, stefan2012, jacobs2011? for similar basic pipeline.

@@

\subsubsection{Compensation for Resolution Effects in Pictor A}

@@

The gain of each channel is the product of an overall instrumental passband and
the spectral dependence of the primary beam in the direction of the source.
Sources sharing the same track through the primary beam will have the same
average spectral gain function resulting from frequency dependent primary beam
attenuation.   We matched each measured source spectrum time sample to the
nearest sample (in altitude/azimuth) of a calibrator source
(J2331-416)\footnote{This source was chosen for the amount of data found in the
literature and the apparent smoothness of the spectrum.}.  We then, average the
% XXX clarify why one source used here, and more sources later 
two matched data streams in time.  Since both tracks make the same slice
through the primary beam, they will have the same average effective gain.
Assuming a power law model for J2331-416 (33Jy $\alpha=-0.76$), we compute a
% XXX I got these parameters for 2331: $S_{150}=31.9\ {\rm Jy}$, $\alpha=-0.69$ 
% XXX forward reference section on fitting spectra for how this was derived for 2331
bandpass gain.  After calibrating the raw 203 channel spectra with this
bandpass, we average into 10MHz sub-bands between 120 and 180 MHz, computing
the standard deviation as an estimate of the error.

@@

% XXX paragraph too remedial. digest
In general an experiment measures data $D$ and given some model of the
statistics of the measurement one usually assigns an error bar defining the
probability of getting that data, given a model $M$.  Given all the new data,
and prior data, there will be a new optimal set of model parameters $M$ with
associated error bars.  In general, these error bars are a parameterization of
a probability distribution function.  The pdf associated with the data often
called the likelihood ($\mathcal{L}$), while the one corresponding the model
error bars is the {\em posterior probability distribution}, $\Prob(M|D)$. They
are related

% XXX too remedial.  digest to 1 senetence
Direct calculation of the posterior is difficult, particularly the
normalization factor, however there is a simple procedure for drawing samples
from the posterior. In this paper we use a Markov Chain Monte Carlo sampler.
Given any current location in parameter space, this algorithm draws a new set
of parameters and computes the relative likelihood increase. If the probability
difference is larger than a number drawn randomly from the set $(0:1]$, the
jump is accepted ---a Metropolis-Hastings step. In the limit of an infinity of
such steps, this process has been shown to converge on the true posterior
distribution.  In practice it is run for a large number of steps until things
appear to stabilize. The best fit model is the median of all the sampled
parameter sets, while the volume containing a well defined fraction of samples
sets the confidence limits.  The oft quoted ``1$\sigma$" probability level
corresponding to a gaussian distribution contains 65\% of the samples. In
practice the contours are not gaussian. Here we choose a slightly more
conservative probability level of 76\%

We fit a spectral power law to catalog values by sampling
a (log) likelihood which assumes Gaussian measurement errors

@@

% XXX connect with text above
A single overall flux scale is computed in a similar way. However, here we add
a single extra gain factor $g$ multiplying all PAPER measurements, and sum over
several sources.

@@
